I am deeply indebted to all those who helped me develop the measurements
presented here. To Bernd Surrow, for his passion and his unwavering support
throughout my graduate career. To Mike Miller, Renee Fatemi, and Frank Simon,
who taught me how to think like a physicist and helped me find my place in STAR.
To Jan Balewski and Joe Seele, for advising me on the finer points of the
analysis in its closing stages, and to all of my fellow MIT RHIC Spin graduate
students, past and present, for their collaboration and occasional
commiseration. Thank you. The greater STAR Collaboration also deserves my
thanks, especially those members contributing to the spin physics program. I
won't forget Carl Gagliardi and Ernst Sichtermann's careful attention to the
detail of this analysis, nor J\'er\^ome Lauret's energetic leadership of the
Software and Computing systems on which I spent so many hours.

I want to express my gratitude to Alan Hoffman and Mike Miller for taking a
chance on starting a company with me, and for making sure that I stuck around to
finish this thesis despite all of the other demands on our time.

I owe a tremendous debt to my parents, who encouraged my inquisitiveness and
provided the kind of loving home one takes for granted when one doesn't know any
better. Thanks to them, to my brothers and sisters, to the Sulens family, my
friends back home and here in Boston, and many others.

Finally, to my wife Hillary, who has been a constant source of support and
encouragement even as she concluded her own doctoral studies and raised our
little baby girl. My greatest joy is knowing what it means to her to see this
day come to pass.
